Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-08-24 paper/paper.Rmd
Updated effect size plot, caption

These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility. To compute a standardized effect size, we converted all one-sample $t$-statistics into a Cohen's $d$ using the formula $d = t/\sqrt{df}$, where $df$ is the degrees of freedom. We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)`]). This estimate should be viewed with caution, however, due to its dependence on one very large effect size estimate ($d > 15$) from a single study.

@@

```{r, fig.cap="Replication effect size (A) and Bayes factor (B), plotted by the original effect size and Bayes factor, respectively. Point size shows replication N (A) and ratio of test degrees of freedom (B), color indicates subjective replication assessments by the authors. Note that the Sofer et al. (2015) replication showed ES and BF too large to plot easily on these axes and is hence excluded.", fig.pos="ht", fig.height=4}

# Note that the sofer paper is off the charts (d > 16) and excluded
p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, 
             aes(color=replicated_TA_factor, size = collected_n)) +
  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 3.5), 
                breaks = c(.2, .5, .8, 1, 2, 3)) +
  scale_y_continuous(limits = c(0, 3.5), 
                breaks = c(.2, .5, .8, 1, 2, 3)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE) +
  xlab("Orig. effect size (d)") + 
  ylab("Rep. effect size (d)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
  scale_size(name = "Rep. N") +
  # scale_color_solarized(guide = FALSE)
  scale_color_solarized(name = "Subjective rep. rating")

>>>>

These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility. To compute a standardized effect size, we converted all one-sample $t$-statistics into a Cohen's $d$ using the formula $d = t/\sqrt{df}$, where $df$ is the degrees of freedom. We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)`]).

@@

```{r, fig.cap="Replication effect size (A) and Bayes factor (B), plotted by the original effect size and Bayes factor, respectively. Point size shows replication N (A) and ratio of test degrees of freedom (B), color indicates subjective replication assessments by the authors. Note that the key statistic in the Sofer et al. (2015) replication was a multivariate $F$ test, hence a default Bayes factor could not be computed.", fig.pos="ht", fig.height=4}

p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, 
             aes(color=replicated_TA_factor, size = collected_n)) +
  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5)) +
  scale_y_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE) +
  xlab("Orig. effect size (d)") + 
  ylab("Rep. effect size (d)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
  scale_size(name = "Rep. N") +
  # scale_color_solarized(guide = FALSE)
  scale_color_solarized(name = "Subjective rep. rating")
